00_datawrangling.Rmd

### 2019-04-19 analysis/00_datawrangling.Rmd
create bird metadata file
better sample export

@@

@@

```{r write}
write.csv(colData_manipluation, "../results/00_colData_manipluation.csv", row.names = TRUE) 
write.csv(countData_manipluation, "../results/00_countData_manipluation.csv", row.names = TRUE) 
write.csv(colData_characterization, "../results/00_colData_characterization.csv", row.names = TRUE) 
write.csv(countData_characterization, "../results/00_countData_characterization.csv", row.names = TRUE) 
write.csv(geneinfo, "../results/00_geneinfo.csv", row.names = TRUE)
```

>>>>

# add variable to distinguish characterization study and manipulation
colData$study <- ifelse(grepl("m.|extend|prolong", colData$treatment), "manipulation", "charcterization")

@@

## save bird data

```{r}
samples <- colData
write.csv(samples, "../metadata/samples.csv")

birds <- colData %>%
  select(bird, sex, treatment) %>%
  distinct()
write.csv(birds, "../metadata/birds.csv")
```

@@

```{r write}
write.csv(colData_manipluation, "../metadata/00_colData_manipluation.csv", row.names = TRUE) 
write.csv(countData_manipluation, "../results/00_countData_manipluation.csv", row.names = TRUE) 
write.csv(colData_characterization, "../metadata/00_colData_characterization.csv", row.names = TRUE) 
write.csv(countData_characterization, "../results/00_countData_characterization.csv", row.names = TRUE) 
write.csv(geneinfo, "../results/00_geneinfo.csv", row.names = TRUE)
```
